---
title: "Burritos Data - plots"
author: "Saurabh Sharma"
date: "November 16, 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Create a variable called ritos and store your data in in.
```{r}
getwd()
ritos = read.csv("Burritos_Data.csv")
```

2. Print the first 6 rows of ritos
```{r}
head(ritos)
```

3. Print the dimension of ritos
```{r}
dim(ritos)
```

4. Filter the data using variable nonSD == 0, store it in ritos and print the dimension of this dataset
```{r}
library(dplyr)
ritos = filter(ritos, NonSD == 0)
dim(ritos)
```

5. Print the number of unique values for Burito variable
```{r}
u = length(unique(ritos$Burrito))
u
```

6. Using the Burito variable, filter data for california and print the number of unique values for the same. Hint : Use grepl to filter 'california'
```{r}
b = table(grepl("california", ritos$Burrito))
length(unique(b))
```

7. Select the variables Location and Yelp and print the first 6 rows
```{r}
r = select(ritos, c(Location,Yelp))
head(r)
```

8. Select columns with Burito ratings i.e. from Tortilla to Wrap and print the first 6 rows
```{r}
as = select(ritos,Tortilla : Wrap)
head(as)
```

9. Create a new data frame df from ritos, select only columns 'Taste', 'Rec',
'Cost', 'Volume
```{r}
df = data.frame(ritos)
select(df, c(Taste,Rec,Cost,Volume))
```

10. Create a new column('Cost_vol') in the same dataframe df using the formula(Cost/Volume), print the first 6 rows of the df
```{r}
h = mutate(df, Cost_vol = Cost/Volume)
h
head(h)
```

11. Select burrito rating variable and recommendation(select variable rec and Tortilla to Taste), store this in a new variable called ing and print the first 6 rows
```{r}
ing = select(ritos, c(Rec,Tortilla : Taste))
ing
```

12. Convert the above data to long format and store in variable df.melt; use 'Rec' and 'Taste' as your id variables, print the structure of this dataset
```{r}
library("UsingR")
library("reshape2")
df.melt = melt(ing, id = c("Rec", "Taste"))
df.melt
structure(df.melt)
```

13. Plot(ggplot and geom_point) the above dataset using x variable 'Taste' and y variable 'Value'
```{r}
ggplot(df.melt, aes(x = Taste, y = value, fill = value)) + geom_point()
```

14. Create a facet_wrap of df.melt use x-axis="Taste", y-axis="Value" and colour = "variable", use geom_point, add a smoother(lm) using geom_smooth, colour the smoother in "black", give the x axis label as 'Burrito Qulaity' and y-axis label as 'score'
```{r}
ggplot(df.melt, aes(x = Taste, y = value, color = variable)) +
  geom_point() +
  geom_smooth(method = "lm", color = "black") +
  facet_wrap(~variable) +
  labs(x = "Burrito Quality", y = "Score")
```
